---
title: "US Stock Market - Complete Sector Analysis"
subtitle: "SPDR Sector ETF Performance + Top Stock Contributors"
author: "Generated via R & Yahoo Finance"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: darkly
    highlight: zenburn
    toc: true
    toc_float:
      collapsed: false
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(quantmod)
library(dplyr)
library(gt)
library(TTR)
library(lubridate)
library(ggplot2)
library(tidyr)
library(htmltools)
```


```{r config, include=FALSE}
# SPDR Sector ETFs
sector_etfs <- data.frame(
  Symbol = c("XLK", "XLI", "XLU", "XLY", "XLF", "XLB", "XLC", "XLV", "XLP", "XLRE", "XLE"),
  Sector = c("Technology", "Industrial", "Utilities", "Consumer Discretionary",
             "Financial", "Materials", "Communication", "Health Care",
             "Consumer Staples", "Real Estate", "Energy"),
  stringsAsFactors = FALSE
)

# Top holdings for each SPDR Sector ETF
sector_holdings <- list(
  XLK = list(name = "Technology",
    stocks = c("AAPL", "MSFT", "NVDA", "AVGO", "CRM", "ORCL", "AMD", "ADBE", "ACN", "CSCO",
               "INTU", "IBM", "TXN", "QCOM", "NOW")),
  XLI = list(name = "Industrial",
    stocks = c("GE", "CAT", "RTX", "UNP", "HON", "DE", "ETN", "ADP", "LMT", "BA",
               "UPS", "GD", "MMM", "ITW", "WM")),
  XLU = list(name = "Utilities",
    stocks = c("NEE", "SO", "DUK", "CEG", "SRE", "AEP", "D", "PCG", "EXC", "XEL",
               "PEG", "ED", "WEC", "AWK", "ES")),
  XLY = list(name = "Consumer Discretionary",
    stocks = c("AMZN", "TSLA", "MCD", "HD", "NKE", "LOW", "BKNG", "SBUX", "TJX", "ABNB",
               "MAR", "GM", "F", "ORLY", "CMG")),
  XLF = list(name = "Financial",
    stocks = c("BRK-B", "JPM", "V", "MA", "BAC", "WFC", "GS", "MS", "SPGI", "AXP",
               "BLK", "C", "SCHW", "CB", "PGR")),
  XLB = list(name = "Materials",
    stocks = c("LIN", "SHW", "APD", "FCX", "ECL", "NEM", "NUE", "VMC", "MLM", "DOW",
               "DD", "PPG", "CTVA", "CE", "IFF")),
  XLC = list(name = "Communication",
    stocks = c("META", "GOOGL", "GOOG", "NFLX", "DIS", "CMCSA", "T", "VZ", "TMUS", "EA",
               "CHTR", "WBD", "OMC", "TTWO", "LYV")),
  XLV = list(name = "Health Care",
    stocks = c("LLY", "UNH", "JNJ", "ABBV", "MRK", "TMO", "ABT", "PFE", "AMGN", "DHR",
               "ISRG", "BMY", "MDT", "SYK", "GILD")),
  XLP = list(name = "Consumer Staples",
    stocks = c("PG", "COST", "WMT", "KO", "PEP", "PM", "MDLZ", "MO", "CL", "GIS",
               "KMB", "STZ", "SYY", "KHC", "HSY")),
  XLRE = list(name = "Real Estate",
    stocks = c("PLD", "AMT", "EQIX", "SPG", "PSA", "O", "WELL", "DLR", "CCI", "VICI",
               "AVB", "EQR", "SBAC", "WY", "ARE")),
  XLE = list(name = "Energy",
    stocks = c("XOM", "CVX", "COP", "EOG", "SLB", "MPC", "PSX", "VLO", "OXY",
               "WMB", "HAL", "DVN", "KMI", "FANG", "TPL"))
)

end_date <- Sys.Date()
start_date_10y <- end_date - years(10)
start_date_1y <- end_date - years(1) - days(5)
```


```{r helper-functions, include=FALSE}
# Trend Strength: 20-day MA momentum
calc_trend_strength <- function(prices, period = 20) {
  if (length(prices) < period + 1) return(0)
  ma <- SMA(prices, n = period)
  ma_clean <- na.omit(ma)
  n <- length(ma_clean)
  if (n <= period) return(0)
  current_ma <- ma_clean[n]
  past_ma <- ma_clean[n - period]
  if (is.na(current_ma) || is.na(past_ma) || past_ma == 0) return(0)
  return(round(((current_ma - past_ma) / past_ma) * 100, 2))
}

get_trend_label <- function(trend_pct) {
  strength <- ifelse(abs(trend_pct) > 2.0, "Strong ", "")
  if (trend_pct > 0.5) return(paste0(strength, "Bullish"))
  if (trend_pct < -0.5) return(paste0(strength, "Bearish"))
  return("Neutral")
}

calc_regime_score <- function(change_pct, trend_pct) {
  score <- 0
  if (change_pct > 1.0) score <- score + 1
  if (change_pct < -1.0) score <- score - 1
  if (trend_pct > 1.0) score <- score + 1
  if (trend_pct < -1.0) score <- score - 1
  if (abs(trend_pct) > 2.5) {
    if (trend_pct > 0) score <- score + 1 else score <- score - 1
  }
  return(max(0, min(3, score + 1)))
}

get_regime_label <- function(score) {
  c("Lagging", "Weakening", "Improving", "Leading")[score + 1]
}

get_row_color <- function(pct) {
  if (pct > 2.0) return("#2d8f2d")
  if (pct > 0.5) return("#4CAF50")
  if (pct > 0) return("#6dbf6d")
  if (pct > -0.5) return("#c8c832")
  if (pct > -1.0) return("#d4a017")
  if (pct > -2.0) return("#e67e22")
  if (pct > -3.5) return("#d35400")
  return("#c0392b")
}

get_stock_row_color <- function(ret) {
  if (ret > 50) return("#1a8c1a")
  if (ret > 30) return("#2d8f2d")
  if (ret > 15) return("#4CAF50")
  if (ret > 5) return("#6dbf6d")
  if (ret > 0) return("#8fbc8f")
  if (ret > -10) return("#d4a017")
  if (ret > -20) return("#e67e22")
  return("#c0392b")
}

# Sector table helper
make_sector_stock_table <- function(etf, results, sector_name) {
  display_df <- results %>%
    select(Rank, Symbol, Last_Price, Return_12M, Return_6M, Return_3M, Return_1M, Pct_From_High) %>%
    rename(`#` = Rank, Price = Last_Price, `12M %` = Return_12M, `6M %` = Return_6M,
           `3M %` = Return_3M, `1M %` = Return_1M, `From 52W Hi` = Pct_From_High)
  
  tbl <- display_df %>%
    gt() %>%
    tab_header(
      title = md(sprintf("**%s (%s) - Top 10 Stocks by 12-Month Return**", etf, sector_name)),
      subtitle = md(sprintf("*%s to %s*", end_date - years(1), end_date))
    ) %>%
    fmt_number(columns = Price, decimals = 2) %>%
    fmt_number(columns = c(`12M %`, `6M %`, `3M %`, `1M %`, `From 52W Hi`),
               decimals = 1, force_sign = TRUE) %>%
    tab_style(style = list(cell_text(color = "white", weight = "bold"),
                            cell_fill(color = "#1a5c1a")),
              locations = cells_title()) %>%
    tab_style(style = list(cell_text(color = "white", weight = "bold"),
                            cell_fill(color = "#333333")),
              locations = cells_column_labels()) %>%
    tab_style(style = cell_text(color = "white"), locations = cells_body()) %>%
    tab_style(style = cell_text(weight = "bold"), locations = cells_body(columns = Symbol)) %>%
    cols_align(align = "center", columns = everything())
  
  for (i in 1:nrow(results)) {
    bg <- get_stock_row_color(results$Return_12M[i])
    tbl <- tbl %>% tab_style(style = cell_fill(color = bg), locations = cells_body(rows = i))
  }
  
  tbl <- tbl %>% tab_options(table.background.color = "#1a1a2e", table.font.size = px(13))
  return(tbl)
}
```


```{r fetch-sector-etf-data, include=FALSE, cache=TRUE}
# ============================================================
# PART 1: Fetch Sector ETF data (10 years)
# ============================================================
etf_data <- list()
for (sym in sector_etfs$Symbol) {
  tryCatch({
    etf_data[[sym]] <- getSymbols(sym, src = "yahoo", from = start_date_10y, to = end_date, auto.assign = FALSE)
  }, error = function(e) { })
}

# Calculate sector ETF metrics
sector_results <- data.frame()

for (i in 1:nrow(sector_etfs)) {
  sym <- sector_etfs$Symbol[i]
  data <- etf_data[[sym]]
  if (is.null(data)) next
  
  prices <- as.numeric(Cl(data))
  n <- length(prices)
  if (n < 252) next
  
  last_price <- round(prices[n], 2)
  prev_price <- prices[n - 1]
  change_pct <- round(((last_price - prev_price) / prev_price) * 100, 2)
  trend_pct <- calc_trend_strength(prices)
  trend_label <- get_trend_label(trend_pct)
  regime_score <- calc_regime_score(change_pct, trend_pct)
  regime_label <- get_regime_label(regime_score)
  
  # Multi-timeframe returns
  ytd_idx <- which(index(data) >= as.Date(paste0(year(end_date), "-01-01")))[1]
  ytd_return <- ifelse(!is.na(ytd_idx),
                        round(((last_price - prices[ytd_idx]) / prices[ytd_idx]) * 100, 2), NA)
  one_yr <- round(((last_price - prices[max(1, n-252)]) / prices[max(1, n-252)]) * 100, 2)
  three_yr <- round(((last_price - prices[max(1, n-756)]) / prices[max(1, n-756)]) * 100, 2)
  five_yr <- round(((last_price - prices[max(1, n-1260)]) / prices[max(1, n-1260)]) * 100, 2)
  ten_yr <- round(((last_price - prices[1]) / prices[1]) * 100, 2)
  
  log_returns <- diff(log(prices))
  vol <- round(sd(tail(log_returns, 252)) * sqrt(252) * 100, 2)
  
  sector_results <- rbind(sector_results, data.frame(
    Symbol = sym, Sector = sector_etfs$Sector[i], Last = last_price,
    Change_Pct = change_pct, Trend_Pct = trend_pct, Trend_Label = trend_label,
    Regime_Score = regime_score, Regime_Label = regime_label,
    YTD_Return = ytd_return, One_Year = one_yr, Three_Year = three_yr,
    Five_Year = five_yr, Ten_Year = ten_yr, Volatility = vol,
    stringsAsFactors = FALSE
  ))
}

sector_results <- sector_results %>% arrange(desc(Change_Pct))
```


```{r fetch-stock-data, include=FALSE, cache=TRUE}
# ============================================================
# PART 2: Fetch individual stock data (12 months)
# ============================================================
fetch_stock_performance <- function(symbol, from_date, to_date) {
  tryCatch({
    data <- getSymbols(symbol, src = "yahoo", from = from_date, to = to_date, auto.assign = FALSE)
    if (is.null(data) || nrow(data) < 20) return(NULL)
    prices <- Cl(data)
    n <- nrow(data)
    current_price <- round(as.numeric(tail(prices, 1)), 2)
    start_price <- as.numeric(prices[1])
    
    data.frame(
      Symbol = symbol,
      Last_Price = current_price,
      Return_12M = round(((current_price - start_price) / start_price) * 100, 2),
      Return_6M = round(((current_price - as.numeric(prices[max(1, n-126)])) /
                          as.numeric(prices[max(1, n-126)])) * 100, 2),
      Return_3M = round(((current_price - as.numeric(prices[max(1, n-63)])) /
                          as.numeric(prices[max(1, n-63)])) * 100, 2),
      Return_1M = round(((current_price - as.numeric(prices[max(1, n-21)])) /
                          as.numeric(prices[max(1, n-21)])) * 100, 2),
      High_52W = round(max(as.numeric(Hi(data)), na.rm = TRUE), 2),
      Low_52W = round(min(as.numeric(Lo(data)), na.rm = TRUE), 2),
      Pct_From_High = round(((current_price - max(as.numeric(Hi(data)), na.rm = TRUE)) /
                              max(as.numeric(Hi(data)), na.rm = TRUE)) * 100, 2),
      stringsAsFactors = FALSE
    )
  }, error = function(e) NULL)
}

all_sector_stocks <- list()
for (etf in names(sector_holdings)) {
  sector_info <- sector_holdings[[etf]]
  sector_results_stocks <- data.frame()
  for (stock in sector_info$stocks) {
    result <- fetch_stock_performance(stock, start_date_1y, end_date)
    if (!is.null(result)) sector_results_stocks <- rbind(sector_results_stocks, result)
    Sys.sleep(0.2)
  }
  if (nrow(sector_results_stocks) > 0) {
    all_sector_stocks[[etf]] <- sector_results_stocks %>%
      arrange(desc(Return_12M)) %>%
      head(10) %>%
      mutate(Rank = row_number())
  }
}

# Combine all stock results
all_stocks_combined <- bind_rows(
  lapply(names(all_sector_stocks), function(etf) {
    all_sector_stocks[[etf]] %>%
      mutate(Sector_ETF = etf, Sector_Name = sector_holdings[[etf]]$name)
  })
)
```


# PART 1: Sector ETF Performance {.tabset}

## Daily Performance

```{r sector-daily-table, echo=FALSE}
daily_df <- sector_results %>%
  mutate(
    `Change %` = sprintf("%+.2f%%", Change_Pct),
    `Trend Strength %` = sprintf("%.2f%% %s", Trend_Pct, Trend_Label),
    `Regime` = sprintf("%d %s", Regime_Score, Regime_Label)
  ) %>%
  select(Symbol, Sector, Last, `Change %`, `Trend Strength %`, Regime)

daily_table <- daily_df %>%
  gt() %>%
  tab_header(title = md("**SPDR SECTOR FUNDs - Daily Performance**"),
             subtitle = sprintf("As of %s", Sys.Date())) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#1a5c1a")),
            locations = cells_title()) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#333333")),
            locations = cells_column_labels()) %>%
  tab_style(style = cell_text(color = "white"), locations = cells_body()) %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_body(columns = Symbol)) %>%
  cols_align(align = "center", columns = c(Symbol, `Change %`, `Trend Strength %`, Regime)) %>%
  cols_align(align = "right", columns = Last)

for (i in 1:nrow(sector_results)) {
  daily_table <- daily_table %>%
    tab_style(style = cell_fill(color = get_row_color(sector_results$Change_Pct[i])),
              locations = cells_body(rows = i))
}

daily_table %>% tab_options(table.background.color = "#1a1a2e", table.font.size = px(14))
```


## Long-Term Returns

```{r sector-longterm-table, echo=FALSE}
lt_df <- sector_results %>%
  arrange(desc(Ten_Year)) %>%
  mutate(
    `YTD` = sprintf("%+.1f%%", YTD_Return),
    `1 Year` = sprintf("%+.1f%%", One_Year),
    `3 Year` = sprintf("%+.1f%%", Three_Year),
    `5 Year` = sprintf("%+.1f%%", Five_Year),
    `10 Year` = sprintf("%+.1f%%", Ten_Year),
    `Vol (Ann.)` = sprintf("%.1f%%", Volatility)
  ) %>%
  select(Symbol, Sector, Last, YTD, `1 Year`, `3 Year`, `5 Year`, `10 Year`, `Vol (Ann.)`)

lt_df %>%
  gt() %>%
  tab_header(title = md("**Sector ETF Long-Term Returns**"),
             subtitle = sprintf("Multi-timeframe returns as of %s | 10 Years of Data", Sys.Date())) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#2c3e50")),
            locations = cells_title()) %>%
  tab_style(style = list(cell_text(color = "white"), cell_fill(color = "#34495e")),
            locations = cells_column_labels()) %>%
  tab_style(style = cell_text(color = "white"), locations = cells_body()) %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_body(columns = Symbol)) %>%
  cols_align(align = "center", columns = everything()) %>%
  tab_options(table.background.color = "#1a1a2e", table.font.size = px(14))
```


## 10-Year Normalized Chart

```{r sector-chart, echo=FALSE, fig.width=14, fig.height=7}
chart_data <- data.frame()
for (sym in names(etf_data)) {
  data <- etf_data[[sym]]
  if (is.null(data)) next
  prices <- Cl(data)
  normalized <- as.numeric(prices) / as.numeric(prices[1]) * 100
  df <- data.frame(Date = index(data), Price = normalized, Symbol = sym, stringsAsFactors = FALSE)
  chart_data <- rbind(chart_data, df)
}
chart_data <- chart_data %>% left_join(sector_etfs, by = "Symbol")

ggplot(chart_data, aes(x = Date, y = Price, color = Symbol)) +
  geom_line(linewidth = 0.8, alpha = 0.85) +
  labs(title = "SPDR Sector ETFs - 10 Year Normalized Performance (Base = 100)",
       subtitle = sprintf("From %s to %s", start_date_10y, end_date),
       x = "", y = "Normalized Price (Base 100)", color = "Sector ETF") +
  theme_dark() +
  theme(
    plot.background = element_rect(fill = "#1a1a2e"),
    panel.background = element_rect(fill = "#16213e"),
    legend.background = element_rect(fill = "#1a1a2e"),
    legend.text = element_text(color = "white", size = 10),
    legend.title = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "#00ff88", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "#aaaaaa"),
    panel.grid.major = element_line(color = "#2a2a4a"),
    panel.grid.minor = element_blank()
  ) +
  geom_hline(yintercept = 100, linetype = "dashed", color = "gray50", alpha = 0.7)
```


# PART 2: Top 10 Stocks Per Sector (12-Month Performance)

## Technology (XLK)

```{r xlk-stocks, echo=FALSE}
make_sector_stock_table("XLK", all_sector_stocks[["XLK"]], "Technology")
```

## Industrial (XLI)

```{r xli-stocks, echo=FALSE}
make_sector_stock_table("XLI", all_sector_stocks[["XLI"]], "Industrial")
```

## Utilities (XLU)

```{r xlu-stocks, echo=FALSE}
make_sector_stock_table("XLU", all_sector_stocks[["XLU"]], "Utilities")
```

## Consumer Discretionary (XLY)

```{r xly-stocks, echo=FALSE}
make_sector_stock_table("XLY", all_sector_stocks[["XLY"]], "Consumer Discretionary")
```

## Financial (XLF)

```{r xlf-stocks, echo=FALSE}
make_sector_stock_table("XLF", all_sector_stocks[["XLF"]], "Financial")
```

## Materials (XLB)

```{r xlb-stocks, echo=FALSE}
make_sector_stock_table("XLB", all_sector_stocks[["XLB"]], "Materials")
```

## Communication (XLC)

```{r xlc-stocks, echo=FALSE}
make_sector_stock_table("XLC", all_sector_stocks[["XLC"]], "Communication")
```

## Health Care (XLV)

```{r xlv-stocks, echo=FALSE}
make_sector_stock_table("XLV", all_sector_stocks[["XLV"]], "Health Care")
```

## Consumer Staples (XLP)

```{r xlp-stocks, echo=FALSE}
make_sector_stock_table("XLP", all_sector_stocks[["XLP"]], "Consumer Staples")
```

## Real Estate (XLRE)

```{r xlre-stocks, echo=FALSE}
make_sector_stock_table("XLRE", all_sector_stocks[["XLRE"]], "Real Estate")
```

## Energy (XLE)

```{r xle-stocks, echo=FALSE}
make_sector_stock_table("XLE", all_sector_stocks[["XLE"]], "Energy")
```


# PART 3: Overall Best & Worst Performers

## Top 20 Best Performing Stocks (All Sectors)

```{r top-20-best, echo=FALSE}
top_20 <- all_stocks_combined %>%
  arrange(desc(Return_12M)) %>%
  head(20) %>%
  mutate(Rank = row_number()) %>%
  select(Rank, Symbol, Sector_Name, Last_Price, Return_12M, Return_6M, Return_3M, Return_1M, Pct_From_High) %>%
  rename(`#` = Rank, Sector = Sector_Name, Price = Last_Price,
         `12M %` = Return_12M, `6M %` = Return_6M, `3M %` = Return_3M,
         `1M %` = Return_1M, `From 52W Hi` = Pct_From_High)

tbl_top <- top_20 %>%
  gt() %>%
  tab_header(title = md("**TOP 20 BEST Performing Stocks Across All Sectors**"),
             subtitle = md(sprintf("*Ranked by 12-Month Return | %s to %s*",
                                   end_date - years(1), end_date))) %>%
  fmt_number(columns = Price, decimals = 2) %>%
  fmt_number(columns = c(`12M %`, `6M %`, `3M %`, `1M %`, `From 52W Hi`),
             decimals = 1, force_sign = TRUE) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#1a5c1a")),
            locations = cells_title()) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#333333")),
            locations = cells_column_labels()) %>%
  tab_style(style = cell_text(color = "white"), locations = cells_body()) %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_body(columns = Symbol)) %>%
  cols_align(align = "center", columns = everything()) %>%
  data_color(columns = `12M %`, palette = c("#f39c12", "#27ae60"), domain = NULL) %>%
  tab_options(table.background.color = "#1a1a2e", table.font.size = px(13))

tbl_top
```


## Top 20 Worst Performing Stocks (All Sectors)

```{r top-20-worst, echo=FALSE}
bottom_20 <- all_stocks_combined %>%
  arrange(Return_12M) %>%
  head(20) %>%
  mutate(Rank = row_number()) %>%
  select(Rank, Symbol, Sector_Name, Last_Price, Return_12M, Return_6M, Return_3M, Return_1M, Pct_From_High) %>%
  rename(`#` = Rank, Sector = Sector_Name, Price = Last_Price,
         `12M %` = Return_12M, `6M %` = Return_6M, `3M %` = Return_3M,
         `1M %` = Return_1M, `From 52W Hi` = Pct_From_High)

tbl_bottom <- bottom_20 %>%
  gt() %>%
  tab_header(title = md("**TOP 20 WORST Performing Stocks Across All Sectors**"),
             subtitle = md(sprintf("*Ranked by 12-Month Return (Ascending) | %s to %s*",
                                   end_date - years(1), end_date))) %>%
  fmt_number(columns = Price, decimals = 2) %>%
  fmt_number(columns = c(`12M %`, `6M %`, `3M %`, `1M %`, `From 52W Hi`),
             decimals = 1, force_sign = TRUE) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#8b0000")),
            locations = cells_title()) %>%
  tab_style(style = list(cell_text(color = "white", weight = "bold"),
                          cell_fill(color = "#333333")),
            locations = cells_column_labels()) %>%
  tab_style(style = cell_text(color = "white"), locations = cells_body()) %>%
  tab_style(style = cell_text(weight = "bold"), locations = cells_body(columns = Symbol)) %>%
  cols_align(align = "center", columns = everything()) %>%
  data_color(columns = `12M %`, palette = c("#c0392b", "#f39c12"), domain = NULL) %>%
  tab_options(table.background.color = "#1a1a2e", table.font.size = px(13))

tbl_bottom
```


# PART 4: Visualizations

## Sector Average Returns (Bar Chart)

```{r sector-bar-chart, echo=FALSE, fig.width=14, fig.height=8}
sector_avg <- all_stocks_combined %>%
  group_by(Sector_ETF, Sector_Name) %>%
  summarize(
    Avg_12M = mean(Return_12M, na.rm = TRUE),
    Best_Stock = Symbol[which.max(Return_12M)],
    Best_Return = max(Return_12M, na.rm = TRUE),
    Worst_Stock = Symbol[which.min(Return_12M)],
    Worst_Return = min(Return_12M, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(Avg_12M))

ggplot(sector_avg, aes(x = reorder(Sector_Name, Avg_12M), y = Avg_12M, fill = Avg_12M)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = sprintf("%+.1f%%", Avg_12M)),
            hjust = ifelse(sector_avg$Avg_12M > 0, -0.1, 1.1),
            color = "white", size = 4) +
  coord_flip() +
  scale_fill_gradient2(low = "#c0392b", mid = "#f39c12", high = "#27ae60", midpoint = 0) +
  labs(title = "Average 12-Month Return by Sector (Top 10 Stocks per Sector)",
       subtitle = sprintf("%s to %s", end_date - years(1), end_date),
       x = "", y = "Average 12-Month Return (%)") +
  theme_dark() +
  theme(
    plot.background = element_rect(fill = "#1a1a2e"),
    panel.background = element_rect(fill = "#16213e"),
    legend.position = "none",
    axis.text = element_text(color = "white", size = 11),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "#00ff88", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "#aaaaaa"),
    panel.grid.major.x = element_line(color = "#2a2a4a"),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank()
  )
```


## Return vs Momentum Scatter

```{r scatter-chart, echo=FALSE, fig.width=12, fig.height=7}
ggplot(all_stocks_combined, aes(x = Return_3M, y = Return_12M, color = Sector_Name)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_text(aes(label = Symbol), size = 2.5, vjust = -0.8, color = "white", alpha = 0.7) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  labs(title = "All Sector Stocks: 12-Month Return vs 3-Month Momentum",
       subtitle = "Top-right = Strong long-term AND recent momentum | Bottom-left = Underperformers",
       x = "3-Month Return (%)", y = "12-Month Return (%)", color = "Sector") +
  theme_dark() +
  theme(
    plot.background = element_rect(fill = "#1a1a2e"),
    panel.background = element_rect(fill = "#16213e"),
    legend.background = element_rect(fill = "#1a1a2e"),
    legend.text = element_text(color = "white", size = 9),
    legend.title = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "#00ff88", size = 14, face = "bold"),
    plot.subtitle = element_text(color = "#aaaaaa"),
    panel.grid.major = element_line(color = "#2a2a4a"),
    panel.grid.minor = element_blank()
  )
```

## Market Summary

```{r market-summary, echo=FALSE}
leading <- sum(sector_results$Regime_Score == 3)
improving <- sum(sector_results$Regime_Score == 2)
weakening <- sum(sector_results$Regime_Score == 1)
lagging <- sum(sector_results$Regime_Score == 0)
avg_change <- mean(sector_results$Change_Pct)
positive <- sum(sector_results$Change_Pct > 0)
negative <- nrow(sector_results) - positive
breadth <- ifelse(positive > negative, "BULLISH",
                  ifelse(negative > positive, "BEARISH", "NEUTRAL"))

best_sector <- sector_avg$Sector_Name[1]
worst_sector <- sector_avg$Sector_Name[nrow(sector_avg)]
```

| Metric | Value |
|--------|-------|
| **Regime: Leading** | `r leading` sectors |
| **Regime: Improving** | `r improving` sectors |
| **Regime: Weakening** | `r weakening` sectors |
| **Regime: Lagging** | `r lagging` sectors |
| **Average Daily Change** | `r sprintf("%+.2f%%", avg_change)` |
| **Market Breadth** | `r positive` up / `r negative` down → **`r breadth`** |
| **Best Sector (12M Avg)** | `r best_sector` (`r sprintf("%+.1f%%", sector_avg$Avg_12M[1])`) |
| **Worst Sector (12M Avg)** | `r worst_sector` (`r sprintf("%+.1f%%", sector_avg$Avg_12M[nrow(sector_avg)])`) |
| **Top Stock Overall** | `r all_stocks_combined$Symbol[which.max(all_stocks_combined$Return_12M)]` (`r sprintf("%+.1f%%", max(all_stocks_combined$Return_12M))`) |
| **Worst Stock Overall** | `r all_stocks_combined$Symbol[which.min(all_stocks_combined$Return_12M)]` (`r sprintf("%+.1f%%", min(all_stocks_combined$Return_12M))`) |

---

*Source: Yahoo Finance | SPDR State Street Global Advisors*
*Generated: `r Sys.time()`*
